### 2018-01-21 response_to_referee.txt

     Moreover, such discussion -- Bayesian vs Frequentist -- has far
     deeper roots. See e.g. Probability theory, the logic of science,
     E.T. Jaynes, Cambridge University Press 2003.

Actually, our problem is with the *names*. We agree with the referee
that these two things are importantly and substantially different!
They have totally different meanings, of course. We have fixed that
all up in the text now, making it clear that these are not the same
thing at ALL. We changed both the footnote (and extended it to make
the point) and also the text that is so footnoted.

     3. Lack of discussion about prediction vs credible intervals.

We interpreted this telegraphic comment to mean: Shouldn't the paper
say something about the fact that you might want to put a
probabilistic interval on a prediction for new data (like a new
observation of a binary star's velocity, given past observations).  We
considered this out of scope, because we don't have much or any
content on decision theory, experimental design, or model
checking. There is lots there, though, and it is deserving of more
attention.

### 2018-01-22 response_to_referee.txt

     Moreover, such discussion -- Bayesian vs Frequentist -- has far
     deeper roots. See e.g. Probability theory, the logic of science,
     E.T. Jaynes, Cambridge University Press 2003.

Actually, our problem is with the *names*. We agree with the referee
that these two things are importantly and substantially different!
They have totally different meanings, of course. We have fixed that
all up in the text now, making it clear that these are not the same
thing at ALL. We changed both the footnote (and extended it to make
the point) and also the text that is so footnoted.

     3. Lack of discussion about prediction vs credible intervals.

We interpreted this telegraphic comment to mean: Shouldn't the paper
say something about the fact that you might want to put a
probabilistic interval on a prediction for new data (like a new
observation of a binary star's velocity, given past observations).  We
put in a mention in the Model Checking subsection. It is certainly
deserving of more attention than it gets here.

@@

     4. Model check

     Lack of contemporary discussion such as e.g. Gabry et
     al. Visualization in Bayesian workflow,
     https://arxiv.org/abs/1709.01449

Ooh that's a great reference! We cite this in the relevant place now,
and were pleased to be pointed at this. Indeed, Gelman has been a
great public voice in support of taking this broader view of what
Bayesian inference is.

@@

     Please consider adding some material about

     Approximate Bayesian Computation, since it has gained space in astronomy e.g.

     https://arxiv.org/abs/1608.07606
     https://arxiv.org/abs/1607.01782 
     https://arxiv.org/abs/1504.06129 
     https://arxiv.org/abs/1202.1426

While we agree that the ABC developments are exciting -- and some of
them are being worked on by us!! -- we do consider this out of
scope. As we now better explain in the paper, we aren't trying to
cover the whole ground of inference, we are just trying to introduce
the uninitiated to the method and help them get over the initial
stumbling blocks. So we have not made a change here.

@@

     ---------------------------------------------------------------------- 
     Statistics Editor Comments:

     As a didactic presentation, I suggest two additions:

     (a) Add a table listing MCMC approaches so the reader appreciates
     the variety of options available
     (e.g. https://www.rdocumentation.org/packages/LaplacesDemon/versions/16.0.1/topics/LaplacesDemon)

We explicitly consider this out of scope, as we have said both early in
the paper, and in the Advanced-Methods section. We call out to much more
comprehensive reviews of methods now, which have these tables and full
descriptions of the methods.

### 2018-01-22 mcmc.tex
issues 4 and 5

Much more informative are methods (like plotting residuals of the data
away from the model in the space of the data) that look at what parts
of the data the model ``explains well'' and what parts of the data the
model ``explains badly''.
These kinds of experiments usually reveal inadequacies of the model in
a rich way, or confirm that certain assumptions are bad.
Cross-validation\note{Cross-validation is an incredibly valuable set
  of techniques that all astronomers should know.
  it is not clear what to cite here, but one possibility is \citet{crossval}.}
is a framework for constructing
valuable tests of this form, as is posterior predictive checks\note{%
  The posterior predictive check is one of the Bayesian equivalents of
  a goodness-of-fit test \citep{ppcheck}.}
Importantly, you want to find ways to compare your model to your data
\emph{in the space of the data}.
Don't just look at the parameter space of your model!
It is the data that really exist, especially when all models are wrong!

There are model checking methods (like varying the prior and
re-running \MCMC) that test the sensitivity of results to assumptions.
Not only are these very valuable for testing the model, they are
essential for writing any paper about your results: The reader always
wants to know the sensitivity of results to assumptions.\note{And be
  sure not to forget that there are (at least) as many assumptions
  encoded in your likelihood function as there are in your prior
  pdfs, probably far more. No data analysis is protected from \emph{subjectivity}.}
Once again, it is important to find ways to display the results of
such tests in the space of the data.
All we will say here about these kinds of rich model tests is that you
should do them, and report the results.

The second---and less important---point about model checking is that
the ur-Bayesian thing to be doing is computing a Bayesian evidence
integral.
However, it is usually inadvisable:
The integral is expensive to compute.
Most \MCMC\ methods are cleverly designed to \emph{avoid} computing this
integral (as we note above in \sectionname~\ref{sec:when}); so it usually adds
expense to the project.
At the end of the day, it returns only a single, scalar number, with
no guidance about how to use it (and indeed there are only heuristics
to reach for).
If your model is wrong, the richer tests of visualization of residuals
or sensitivity to assumptions are much more likely to lead to insight
about what changes to make or what new directions to explore.

@@

>>>>

Much more informative are methods (like plotting residuals of the data
away from the model in the space of the data) that look at what parts
of the data the model ``explains well'' and what parts of the data the
model ``explains badly''.
These kinds of experiments usually reveal inadequacies of the model in
a rich way, or confirm that certain assumptions are bad.
Cross-validation\note{Cross-validation is an incredibly valuable set
  of techniques that all astronomers should know.
  it is not clear what to cite here, but one possibility is \citet{crossval}.}
is a framework for constructing
valuable tests of this form, as is posterior predictive checking.\note{%
  The posterior predictive check is one of the Bayesian equivalents of
  a goodness-of-fit test \citep{ppcheck}.}
Indeed, making posterior predictions of new data, and testing the
model by taking completely new data and comparing to those predictions,
is the strongest test of any model. Each sample from the \MCMC\ chain
provides a prediction for future data; the distribution over these sample
predictions is the posterior prediction for new data.
Importantly, you want to find ways to compare your model to your data
\emph{in the space of the data}.
Don't just look at the parameter space of your model. Look at the data.
It is the data that really exist, especially when all models are wrong!

There are model checking methods (like varying the prior or assumptions
in the likelihood function and
re-running \MCMC) that test the sensitivity of results to assumptions.
Not only are these very valuable for testing the model, they are
essential for writing any paper about your results: The reader always
wants to know the sensitivity of results to assumptions.\note{And be
  sure not to forget that there are (at least) as many assumptions
  encoded in your likelihood function as there are in your prior
  pdfs, probably far more. No data analysis is protected from \emph{subjectivity}.}
Once again, it is important to find ways to display the results of
such tests in the space of the data.
All we will say here about these kinds of rich model tests is that you
should do them, and report the results.

The second---and less important---point about model checking is that
the ur-Bayesian thing to be doing is computing a Bayesian evidence
integral.
However, it is usually inadvisable:
The integral is expensive to compute.
Most \MCMC\ methods are cleverly designed to \emph{avoid} computing this
integral (as we note above in \sectionname~\ref{sec:when}); so it usually adds
expense to the project.
At the end of the day, it returns only a single, scalar number, with
no guidance about how to use it (and indeed there are only heuristics
to reach for).
If your model is wrong, the richer tests of visualization of residuals
or sensitivity to assumptions are much more likely to lead to insight
about what changes to make or what new directions to explore.\footnote{%
  There is a growing idea that Bayesian inference---and inference in general---is
  about much more than inferring parameter values: It is about understanding and
  elaborating models (for example, \citealt{gabry}).}

@@

\bibitem[Gabry \etal(2017)]{gabry}
  Gabry, J., Simpson, D., Vehtari, A., Betancourt, M., \& Gelman, A., 2017,
  {Visualization in Bayesian workflow},
  \arxiv{1709.01449}.
